The most obvious approach to attacking this application would be to eavesdrop on the communication channel and just capture and read the traffic. This is not possible since as mentioned beforehand all traffic apart from the header and initialization messages is encrypted using symmetric cipher AES-GCM-256.

However, more complex approaches could be used for breaking the security of this application. One of those approaches is the impersonation of a communicating entity, in this case, one of the peers. The use of public key cryptography, more specifically digital signatures prevents the use of this approach. An attacker impersonating the client can't create a valid client init message since he can't create a digital signature that would be verifiable by the server. Only the real client can create that signature since he has the private key. Similarly, if the attacker would impersonate the server, he can't create a valid server init message since only the client holds the valid private key to the shared public key.

Another type of attack is the MitM (\acl{MITM}) attack. It happens when an attacker manages to create two simultaneous connections between the user and the server. The peers think they are communicating with each other, in truth the attacker is just forwarding their messages back and forth while being able to read them. To prevent this type of attack, the digital signature is again used together with the preconfigured keys. If the attacker wants to create a separate connection with the server after receiving the client init message from the client, the only thing he can do is forward it through to the server, which is harmless. He can't edit it or change the value for example of the public encryption key since he can't create a new signature. He is also unable to impersonate the server since he doesn't know his private key.
