The results of the optimization process described in Section \ref{sec:optimizing} for booth Kyber and Dilithium can be seen in Tables \ref{tab:kem_sum} and \ref{tab:dil_sum}. The tables compare the average speed of each algorithm measured using benchmarks for two implementations. The Circl\footnote{\url{https://github.com/cloudflare/circl}} implementation is a cryptography library created by Cloudflare. The implementation of Kyber and Dilithium in this thesis is called PqCom. The process of benchmarking included key generation, encapsulation, decapsulation for Kyber and key generation, signature creation, and verification for Dilithium. The benchmarks were run on an AMD Ryzen 5 3600 processor.

\object{tab}{tables/kem_sum.tex}{KEMs preformance summary}{tab:kem_sum}
\object{tab}{tables/dil_sum.tex}{Digital signatures preformance summary}{tab:dil_sum}

More detailed benchmarks can also be found in Appendix \ref{ch:performance} where each table contains the performance information about one implementation of an algorithm, all of its modes and also measurements of its sub algorithms. Each table also contains comparisons to other models of processors. The exact command that was used to benchmark is
\begin{itemize}
  \item \texttt{go test -bench="Kem|Signature" -run=\^{}\# -count=20 -timeout=24h \textbackslash\\ ./... | tee out.txt}
\end{itemize}
This command runs benchmarks defined in Appendix \ref{ch:available_algs}. Each benchmark is run 20 times to reduce the amount of statistical noise. The output is written to the file \texttt{out.txt}. This file is then parsed with \texttt{benchstat} application mentioned in Section \ref{sec:cmd_benchmark}.
