In order to fully understand how any application that creates a communication channel between two entites works, it is important to firtly look at the concepts of network basics. The contents of this chapter will focus on the topis such as the TCP/IP protocol suite, TCP (\acl{TCP}), UDP (\acl{UDP}) protocols and differenes between client-server and peer-to-peer communications.

The TCP/IP protocol suit consists of 5 layers as can be seed in table \ref{tab:tcp_ip_table}. Each layer is defined by one or more protocols. A protocol defines strict rules for what, how and when should an entity communicate. Each row in the TCP/IP suite contains atleast one protocol, which again dictates how the communication should proceed on that layer. A protocol layer communicates horizontally with other protocol layers using PDUs (\acl{PDU}), each PDU is either encapsulated or deencapsulated into another PDU, depending on way the data is flowing through the TCP/IP layers. During this process a new header is added or removed. A header contains important information fot that specific layer. For example the IP address is contained in the header for the network layer. The layers also communicate vertically using either physical channels (physical and data link layers) or virtual channels (all other layers). Psysical channels are created between a physical medium by whitch the bits travels through, virtual channels on the other hand are created between applications or more complex diveces like routers. Channels on each layer use a different identifier to differencieate between them. Aformentioned information for each layer can be found in table \ref{tab:tcp_ip_table}.

\object{tab}{tables/tcp_ip_details}{TCP/IP protocol suite}{tab:tcp_ip_table}


% Describe network basics such as TCP 3 way handshake, UDP and so on.

TODO: cite
